Probabilistic Model of Bilateral Lymphatic Spread in Head and Neck Cancer

### 2024-12-10 .output/_tex/manuscript.tex
fix data stratification table

\caption{}\label{T_c6cfe}\tabularnewline
\toprule\noalign{}
Institution & Total & Age (median) & Neck Dissection & N0 & Early T-Cat.
& Mid. Ext. \\
\midrule\noalign{}
\endfirsthead
\toprule\noalign{}
Institution & Total & Age (median) & Neck Dissection & N0 & Early T-Cat.
& Mid. Ext. \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
Centre Léon Bérard & 325 & 60 & 100\% & 19\% & 69\% & 18\% \\
Inselspital Bern & 74 & 61 & 100\% & 18\% & 66\% & 14\% \\
University Hospital Zurich & 287 & 66 & 26\% & 18\% & 52\% & 31\% \\
Vall d\textquotesingle Hebron Barcelona Hospital & 147 & 58 & 5\% & 21\%
& 34\% & 34\% \\

@@

\caption{}\label{T_da35b}\tabularnewline
\toprule\noalign{}
Parameter & Mean & Std. Dev. \\
\midrule\noalign{}
\endfirsthead
\toprule\noalign{}
Parameter & Mean & Std. Dev. \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
Mid. ext. probability & 8.16\% & ± 0.48\% \\
ipsi: T ➜ I & 2.80\% & ± 0.26\% \\
ipsi: T ➜ II & 34.89\% & ± 1.40\% \\
ipsi: T ➜ III & 5.45\% & ± 0.66\% \\
ipsi: T ➜ IV & 0.94\% & ± 0.18\% \\
ipsi: T ➜ V & 1.83\% & ± 0.22\% \\
ipsi: T ➜ VII & 2.32\% & ± 0.26\% \\
contra: T ➜ I & 0.29\% & ± 0.09\% \\
contra: T ➜ II & 2.46\% & ± 0.29\% \\
contra: T ➜ III & 0.14\% & ± 0.07\% \\
contra: T ➜ IV & 0.19\% & ± 0.08\% \\
contra: T ➜ V & 0.05\% & ± 0.04\% \\
contra: T ➜ VII & 0.50\% & ± 0.17\% \\
Mixing ⍺ & 33.87\% & ± 4.32\% \\
I ➜ II & 62.50\% & ± 16.69\% \\
II ➜ III & 14.23\% & ± 1.64\% \\
III ➜ IV & 15.86\% & ± 1.93\% \\
IV ➜ V & 14.58\% & ± 3.76\% \\
late T-cat. binom. prob. & 44.98\% & ± 1.99\% \\

@@

\caption{}\label{T_22819}\tabularnewline
\toprule\noalign{}
T-cat. & ipsi & Mid. ext. & \multicolumn{2}{l}{%
I} & \multicolumn{2}{l}{%
II} & \multicolumn{2}{l}{%
III} & \multicolumn{2}{l}{%
IV} & total \\
& & & n & \% & n & \% & n & \% & n & \% & n \\
\midrule\noalign{}
\endfirsthead
\toprule\noalign{}
T-cat. & ipsi & Mid. ext. & \multicolumn{2}{l}{%
I} & \multicolumn{2}{l}{%
II} & \multicolumn{2}{l}{%
III} & \multicolumn{2}{l}{%
IV} & total \\
& & & n & \% & n & \% & n & \% & n & \% & n \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
early & 0 & False & 0 & 1 & 0 & 0 & 0.00 & 1.16 & 0.00 & 0.00 & 86 \\
early & 0 & True & 0 & 1 & 1 & 0 & 0.00 & 10.00 & 10.00 & 0.00 & 10 \\
early & 0 & nan & 0 & 0 & 0 & 0 & 0.00 & 0.00 & 0.00 & 0.00 & 12 \\
early & 1 & False & 1 & 11 & 2 & 1 & 0.53 & 5.82 & 1.06 & 0.53 & 189 \\
early & 1 & True & 1 & 2 & 0 & 0 & 11.11 & 22.22 & 0.00 & 0.00 & 9 \\
early & 1 & nan & 0 & 3 & 0 & 1 & 0.00 & 9.68 & 0.00 & 3.23 & 31 \\
early & ≥ 2 & False & 1 & 15 & 3 & 3 & 0.96 & 14.42 & 2.88 & 2.88 &
104 \\
early & ≥ 2 & True & 0 & 3 & 4 & 1 & 0.00 & 30.00 & 40.00 & 10.00 &
10 \\
early & ≥ 2 & nan & 0 & 3 & 0 & 0 & 0.00 & 13.64 & 0.00 & 0.00 & 22 \\
advanced & 0 & False & 0 & 2 & 0 & 0 & 0.00 & 5.88 & 0.00 & 0.00 & 34 \\
advanced & 0 & True & 0 & 3 & 0 & 0 & 0.00 & 12.50 & 0.00 & 0.00 & 24 \\
advanced & 0 & nan & 0 & 0 & 0 & 0 & 0.00 & 0.00 & 0.00 & 0.00 & 3 \\
advanced & 1 & False & 0 & 3 & 0 & 0 & 0.00 & 4.55 & 0.00 & 0.00 & 66 \\
advanced & 1 & True & 1 & 18 & 5 & 1 & 1.64 & 29.51 & 8.20 & 1.64 &
61 \\
advanced & 1 & nan & 0 & 0 & 0 & 0 & 0.00 & 0.00 & 0.00 & 0.00 & 9 \\
advanced & ≥ 2 & False & 4 & 16 & 7 & 4 & 5.26 & 21.05 & 9.21 & 5.26 &
76 \\
advanced & ≥ 2 & True & 3 & 46 & 18 & 8 & 3.80 & 58.23 & 22.78 & 10.13 &
79 \\
advanced & ≥ 2 & nan & 0 & 0 & 0 & 0 & 0.00 & 0.00 & 0.00 & 0.00 & 8 \\

>>>>

\caption{}\label{T_6831a}\tabularnewline
\toprule\noalign{}
Institution & Total & Age (median) & Neck Dissection & N0 & Early T-Cat.
& Mid. Ext. \\
\midrule\noalign{}
\endfirsthead
\toprule\noalign{}
Institution & Total & Age (median) & Neck Dissection & N0 & Early T-Cat.
& Mid. Ext. \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
Centre Léon Bérard & 325 & 60 & 100\% & 19\% & 69\% & 18\% \\
Inselspital Bern & 74 & 61 & 100\% & 18\% & 66\% & 14\% \\
University Hospital Zurich & 287 & 66 & 26\% & 18\% & 52\% & 31\% \\
Vall d\textquotesingle Hebron Barcelona Hospital & 147 & 58 & 5\% & 21\%
& 34\% & 34\% \\

@@

\caption{}\label{T_fedc5}\tabularnewline
\toprule\noalign{}
Parameter & Mean & Std. Dev. \\
\midrule\noalign{}
\endfirsthead
\toprule\noalign{}
Parameter & Mean & Std. Dev. \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
Mid. ext. probability & 8.16\% & ± 0.48\% \\
ipsi: T ➜ I & 2.80\% & ± 0.26\% \\
ipsi: T ➜ II & 34.89\% & ± 1.40\% \\
ipsi: T ➜ III & 5.45\% & ± 0.66\% \\
ipsi: T ➜ IV & 0.94\% & ± 0.18\% \\
ipsi: T ➜ V & 1.83\% & ± 0.22\% \\
ipsi: T ➜ VII & 2.32\% & ± 0.26\% \\
contra: T ➜ I & 0.29\% & ± 0.09\% \\
contra: T ➜ II & 2.46\% & ± 0.29\% \\
contra: T ➜ III & 0.14\% & ± 0.07\% \\
contra: T ➜ IV & 0.19\% & ± 0.08\% \\
contra: T ➜ V & 0.05\% & ± 0.04\% \\
contra: T ➜ VII & 0.50\% & ± 0.17\% \\
Mixing ⍺ & 33.87\% & ± 4.32\% \\
I ➜ II & 62.50\% & ± 16.69\% \\
II ➜ III & 14.23\% & ± 1.64\% \\
III ➜ IV & 15.86\% & ± 1.93\% \\
IV ➜ V & 14.58\% & ± 3.76\% \\
late T-cat. binom. prob. & 44.98\% & ± 1.99\% \\

@@

\caption{}\label{T_89008}\tabularnewline
\toprule\noalign{}
T-cat. & ipsi & Mid. ext. & \multicolumn{2}{l}{%
I} & \multicolumn{2}{l}{%
II} & \multicolumn{2}{l}{%
III} & \multicolumn{2}{l}{%
IV} & total \\
& & & n & \% & n & \% & n & \% & n & \% & n \\
\midrule\noalign{}
\endfirsthead
\toprule\noalign{}
T-cat. & ipsi & Mid. ext. & \multicolumn{2}{l}{%
I} & \multicolumn{2}{l}{%
II} & \multicolumn{2}{l}{%
III} & \multicolumn{2}{l}{%
IV} & total \\
& & & n & \% & n & \% & n & \% & n & \% & n \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
early & 0 & False & 0 & 0.00 & 1 & 1.16 & 0 & 0.00 & 0 & 0.00 & 86 \\
early & 0 & True & 0 & 0.00 & 1 & 10.00 & 1 & 10.00 & 0 & 0.00 & 10 \\
early & 0 & nan & 0 & 0.00 & 0 & 0.00 & 0 & 0.00 & 0 & 0.00 & 12 \\
early & 1 & False & 1 & 0.53 & 11 & 5.82 & 2 & 1.06 & 1 & 0.53 & 189 \\
early & 1 & True & 1 & 11.11 & 2 & 22.22 & 0 & 0.00 & 0 & 0.00 & 9 \\
early & 1 & nan & 0 & 0.00 & 3 & 9.68 & 0 & 0.00 & 1 & 3.23 & 31 \\
early & ≥ 2 & False & 1 & 0.96 & 15 & 14.42 & 3 & 2.88 & 3 & 2.88 &
104 \\
early & ≥ 2 & True & 0 & 0.00 & 3 & 30.00 & 4 & 40.00 & 1 & 10.00 &
10 \\
early & ≥ 2 & nan & 0 & 0.00 & 3 & 13.64 & 0 & 0.00 & 0 & 0.00 & 22 \\
advanced & 0 & False & 0 & 0.00 & 2 & 5.88 & 0 & 0.00 & 0 & 0.00 & 34 \\
advanced & 0 & True & 0 & 0.00 & 3 & 12.50 & 0 & 0.00 & 0 & 0.00 & 24 \\
advanced & 0 & nan & 0 & 0.00 & 0 & 0.00 & 0 & 0.00 & 0 & 0.00 & 3 \\
advanced & 1 & False & 0 & 0.00 & 3 & 4.55 & 0 & 0.00 & 0 & 0.00 & 66 \\
advanced & 1 & True & 1 & 1.64 & 18 & 29.51 & 5 & 8.20 & 1 & 1.64 &
61 \\
advanced & 1 & nan & 0 & 0.00 & 0 & 0.00 & 0 & 0.00 & 0 & 0.00 & 9 \\
advanced & ≥ 2 & False & 4 & 5.26 & 16 & 21.05 & 7 & 9.21 & 4 & 5.26 &
76 \\
advanced & ≥ 2 & True & 3 & 3.80 & 46 & 58.23 & 18 & 22.78 & 8 & 10.13 &
79 \\
advanced & ≥ 2 & nan & 0 & 0.00 & 0 & 0.00 & 0 & 0.00 & 0 & 0.00 & 8 \\
